The Astropy Project:

### 2017-09-20 main.tex
Update on Overleaf.

@@

\section{Notes and guidelines (to be removed)}

\begin{itemize}
	\item Right now, we don't foresee needing to include code in this paper. But, if you think you will need to include code in your section, please add it to a separate Python module (.py file) and include it in this repository. 
\end{itemize}

\section{Introduction} \label{sec:intro}

Moritz volunteered to write the intro

\section{Major concepts}
\subsection{Astropy development model, astropy ecosystem}
This subsection should include some basic statistics about the contributors, commits, line of code etc. up to the 2.0 release when we know it.
\subsection{Mixin}
\subsection{Accuracy testing across many different implementation}
\subsection{Use of Quantities across package}

@@

\textbf{Key features}

\begin{itemize}
	\item Celestial coordinates, and local coordinates (via EarthLocation + Time)
	\item JPL ephemerids
\end{itemize}

@@

incl logarithmic units and magnitudes
speed improvements,
interaction with numpy arrays

>>>>

\newcommand{\escapecmd}[1]{\texttt{\detokenize{#1}}}

@@

\section*{Notes and guidelines (\textit{to be removed})}

\begin{itemize}
	\item We don't plan on including code in this paper, but if you think you will need to include code in your section, please add it to a separate Python module (.py file) and include it in this repository. 
    \item Use \escapecmd{\sectionname} not Section, \escapecmd{\figname} not Figure, \escapecmd{\documentname} not Article
\end{itemize}

\section{Introduction} \label{sec:intro}
% Moritz (first draft)

\section{Major concepts}

\subsection{Astropy development model, astropy ecosystem}
This subsection should include some basic statistics about the contributors, commits, line of code etc. up to the 2.0 release when we know it.

\subsection{Mixin}

\subsection{Accuracy testing across many different implementation}

\subsection{Use of Quantities across package}

@@

\textbf{Key features:}
\begin{itemize}
	\item Celestial coordinates, and local coordinates (via EarthLocation + Time)
	\item JPL ephemerids
\end{itemize}

@@

\textbf{Key features:}
\begin{itemize}
	\item incl logarithmic units and magnitudes
	\item speed improvements
    \item interaction with numpy arrays
\end{itemize}
